---
title: "ExperimentResults"
output: html_document
---

This R-Markdown document does the data analysis for my replication study.


Read in the initial data and make a plot
```{r}
data <- read.csv("/Users/Eric/Desktop/Psych254/ehermannProject/Batch_123323_batch_results.csv")
df <- data.frame(data$Answer.personalFinanceClaimScore, data$Answer.overclaimingScore, data$Answer.FLQuizScore, data$Answer.accuracy, data$Answer.personalFinanceFirst)
plot(df$data.Answer.personalFinanceClaimScore, df$data.Answer.overclaimingScore)
```


Get the mean and SD of people's claimed knowledge about personal finance.
```{r}
mean(df$data.Answer.personalFinanceClaimScore)
sd(df$data.Answer.personalFinanceClaimScore)
```

Get b, t value and p for relationship between claimed financial knowledge and overclaiming
```{r}
data.lm = lm(formula = df$data.Answer.overclaimingScore ~ df$data.Answer.personalFinanceClaimScore + df$data.Answer.accuracy, data = df)
summary(data.lm)
```


Get mean and SD for data when personal financial knowledge questions are before the 15 items, and vice versa.
```{r}
personalFinanceFirstData <- df[df$data.Answer.personalFinanceFirst == 1,]
itemQuestionsFirstData <- df[df$data.Answer.personalFinanceFirst == 0,]
mean(personalFinanceFirstData$data.Answer.overclaimingScore)
sd(personalFinanceFirstData$data.Answer.overclaimingScore)
mean(itemQuestionsFirstData$data.Answer.overclaimingScore)
sd(itemQuestionsFirstData$data.Answer.overclaimingScore)
```

Get slope, t value and p for relationship between order and overclaiming
```{r}
order.lm = lm(formula = df$data.Answer.overclaimingScore ~ df$data.Answer.personalFinanceFirst, data = df)
summary(order.lm)
```

Get slope, t value and p for data when personal finance questions are asked first only.
```{r}
PFFirst.lm = lm(formula = personalFinanceFirstData$data.Answer.overclaimingScore ~ personalFinanceFirstData$data.Answer.personalFinanceClaimScore + personalFinanceFirstData$data.Answer.accuracy, data = personalFinanceFirstData)
summary(PFFirst.lm)
```

Get slope, t value and p for data when 15 item questions are asked first only.
```{r}
itemsFirst.lm = lm(formula = itemQuestionsFirstData$data.Answer.overclaimingScore ~ itemQuestionsFirstData$data.Answer.personalFinanceClaimScore + itemQuestionsFirstData$data.Answer.accuracy, data = personalFinanceFirstData)
summary(itemsFirst.lm)
```

Get slope, t value and p for relationship between genuine financial knowledge and overclaiming
```{r}
genuineKnowledge.lm = lm(formula = df$data.Answer.overclaimingScore ~ df$data.Answer.FLQuizScore, data = df)
summary(genuineKnowledge.lm)
```

Get slope, t value and p for relationship between genuine financial knowledge and perceived financial knowledge
```{r}
perceivedKnowledge.lm = lm(formula = df$data.Answer.personalFinanceClaimScore ~ df$data.Answer.FLQuizScore, data = df)
summary(perceivedKnowledge.lm)
```
